Comparing OTU quality across clustering strategies

### 2021-05-12 exploratory/2021/compare-strategies_2021-05.Rmd
Create version of otu quality plot with patchwork

# using facet_grid()

@@

## using cowplot

@@

>>>>

## facet_grid()

@@

## cowplot

@@

Idea: add vsearch _de novo_ & gg to the plot?

## patchwork

```{r otu-quality_patchwork}
library(patchwork)

(mcc_plot  + 
  guides(color = guide_legend(nrow = 1)) +
  theme(legend.position = "bottom")) / 
frac_plot / 
  guide_area() + 
  plot_layout(guides = 'collect') +
  plot_annotation(caption = "dashed line: _de novo_ clustering",
                  tag_levels = 'A',
                  theme = theme(plot.caption = element_markdown()))
```

- [ ] reduce the whitespace
- [ ] figure out how to get the caption & legend side-by-side
